### 2024-09-23 paper-icict24-automatic_summarisation_of_zambian_legislative_documents.tex
Anonymised Paper Template
Anonymised authors and associated affiliations

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
%Template version as of 6/27/2024

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Conference Paper Title*\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured for https://ieeexplore.ieee.org  and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} FName1 LName1}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
fname1.lname1@institution.xx}
\and
\IEEEauthorblockN{2\textsuperscript{nd} FName2 LName2}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
fname2.lname2@institution.xx}
\and
\IEEEauthorblockN{3\textsuperscript{rd} FName3 LName3}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
fname3.lname3@institution.xx}
\and
\IEEEauthorblockN{4\textsuperscript{th} FName4 LName4}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
fname4.lname4@institution.xx}
\and
\IEEEauthorblockN{5\textsuperscript{th} FName5 LName5}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
fname5.lname5@institution.xx}
}

\maketitle

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert.
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits. For more information about how to become an IEEE Conference author or how to write your paper, please visit   IEEE Conference Author Center website: https://conferences.ieeeauthorcenter.ieee.org/.

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA} to \ref{FAT} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}\label{AAA}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}\label{ITH}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}\label{FAT}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

% % % % % \begin{figure}[htbp]
% % % % % \centerline{\includegraphics{fig1.png}}
% % % % % \caption{Example of a figure caption.}
% % % % % \label{fig}
% % % % % \end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\bibitem{b8} D. P. Kingma and M. Welling, ``Auto-encoding variational Bayes,'' 2013, arXiv:1312.6114. [Online]. Available: https://arxiv.org/abs/1312.6114
\bibitem{b9} S. Liu, ``Wi-Fi Energy Detection Testbed (12MTC),'' 2023, gitHub repository. [Online]. Available: https://github.com/liustone99/Wi-Fi-Energy-Detection-Testbed-12MTC
\bibitem{b10} ``Treatment episode data set: discharges (TEDS-D): concatenated, 2006 to 2009.'' U.S. Department of Health and Human Services, Substance Abuse and Mental Health Services Administration, Office of Applied Studies, August, 2013, DOI:10.3886/ICPSR30122.v2
\bibitem{b11} K. Eves and J. Valasek, ``Adaptive control for singularly perturbed systems examples,'' Code Ocean, Aug. 2023. [Online]. Available: https://codeocean.com/capsule/4989235/tree
\end{thebibliography}

\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2024-09-23 paper-icict24-automatic_summarisation_of_zambian_legislative_documents.tex
Added Abstract to Paper
Added IEEE abstract
Added initial Intent to Submit content

@@
 
-\title{Conference Paper Title*\\
-{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured for https://ieeexplore.ieee.org  and
-should not be used}
-\thanks{Identify applicable funding agency here. If none, delete this.}
-}
+\title{Accessible Legislative Information: Automatic Summarisation of Zambian Legislative Documents}
 
@@
 \begin{abstract}
-This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract.
+The National Assembly of Zambia produces a number of important legislative documents which are publicly accessible via its Website.
+One of the documents published by the National Assembly of Zambia are Bills and Acts, which all form the Laws of Zambia.
+The Acts and Bills are ideally meants to be open and accessible to the general citizenery, however, prior studies conducted have highlighted the lack of ease of access and difficulties with interpretation of such documents and the two main barriers to enabling open and accessible legal information.
+This paper presents a potentially viable solution to addressing the chellenges with facilitating open and accessible legislative documents by leveraging the use of Natural Language Processing techniques for automatically summarising legislative documents.
+Specifically, the study was aimed at examinting barriers faced by individuals when comprehending legislative documents and, additionally, determining the feasibility of implementing NLP modules capable of generating concise summaries of legislative documents.
+In order to understand challenges faced when comprehending legal documents, 150 undergraduate students were sampled from the University of Zambia using random sampling.
+To determine the feasibility of using NLP techniques to provide concise summaries of legislative documents, two (2) NLP models—an abstractive summarisation model and extractive summarisation model.
+A human evaluation strategy was used to perform a comparative evaluation of the two (2) NLP models, in order to determine the more effective approach.
+A significant portion—approximately 74.29\%—of participants reported 'Never' (33.99\%) or 'Rarely' (40.3\%) engaging with legislative documents.
+In contrast, (25.71\%) indicated frequent or very frequent interaction.
+This distribution underscores a significant gap in familiarity and engagement with Zambian legislative materials among the study participants.
+In assessing participants' overall understanding of legal documents, the majority (43.5\%) expressed a neutral perception, suggesting that they found these documents neither easy nor hard to understand.
+The majority of the human evaluators had a preference for the abstractive summarisation model, indicating that its brevity, simplicity, and directness as reasons for their choice.
+In addition, the results of the abstractive summarisation model were stated as being easier to understand..
 \end{abstract}

### 2024-09-23 paper-icict24-automatic_summarisation_of_zambian_legislative_documents.tex
Introduction Section
Added content to Introduction section

@@
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+%
+%
+% Sepetmber 23 2024
+\usepackage{cleveref}
+
 \begin{document}
@@
 \section{Introduction}
-This document is a model and instructions for \LaTeX.
-Please observe the conference page limits.
-For more information about how to become an IEEE Conference author or how to write your paper, please visit   IEEE Conference Author Center website: https://conferences.ieeeauthorcenter.ieee.org/.
+\label{sec:introduction}
+The National Assembly of Zambia is mandated by law to “To execute the legislative, oversight, representative and budgetary functions for enhanced democratic governance” \cite{NationalAssembly2023Objectives}.
+In the 2022-2026 strategic plan \cite{NationalAssembly2021Strategic}, the “Strategic Objective 2.2” aims to “Enhance Public Perceptions of the National Assembly” by making parliament open and accessible to the public and, additionally strengthening ICT platforms for public engagement.
 
-\subsection{Maintaining the Integrity of the Specifications}
+While parliament, and entities such as the Zambia Legal Information Institute (ZambiaLII) \cite{ZambiaLII2024Website}, publicly makes available important legislation, interpretation of the documents is problematic due to the size of the documents and the vocabulary used.
+Masson and Tahir report that the barriers associated with providing open and accessible legal information relies on two factors: ease of access and the capacity to interpret the documents \cite{Masson2016Legal}.
 
-The IEEEtran class file is used to format your paper and style the text. All margins, 
-column widths, line spaces, and text fonts are prescribed; please do not 
-alter them. You may note peculiarities. For example, the head margin
-measures proportionately more than is customary. This measurement 
-and others are deliberate, using specifications that anticipate your paper 
-as one part of the entire proceedings, and not as an independent document. 
-Please do not revise any of the current designations.
+This paper is organised as follows: \Cref{sec:introduction} provides context and background information associated with the studies conducted; \Cref{sec:related_work} comprehensively discusses existing work; \Cref{sec:methodology} outlines the methodological approaches employed when conducting the studies; \Cref{sec:results_and_discussion} discusses the findings and, finally, \Cref{sec:conclusion} outlines concluding remarks and potential future work.
 
-\section{Prepare Your Paper Before Styling}
-Before you begin to format your paper, first write and save the content as a 
-separate text file. Complete all content and organizational editing before 
-formatting. Please note sections \ref{AA} to \ref{FAT} below for more information on 
-proofreading, spelling and grammar.
+\section{Related Work}
+\label{sec:related_work}
+Xxxxx xxxxx xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx.
 
-Keep your text and graphic files separate until after the text has been 
-formatted and styled. Do not number text heads---{\LaTeX} will do that 
-for you.
+\section{Methodology}
+\label{sec:methodology}
+Xxxxx xxxxx xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx.
 
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text, 
-even after they have been defined in the abstract. Abbreviations such as 
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-abbreviations in the title or heads unless they are unavoidable.
+\section{Results and Discussion}
+\label{sec:results_and_discussion}
+Xxxxx xxxxx xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx.
 
-\subsection{Units}
-\begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-\end{itemize}
+\section{Conclusions and Future Work}
+\label{sec:conclusion}
+Xxxxx xxxxx xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx.
 
-\subsection{Equations}
-Number equations consecutively. To make your 
-equations more compact, you may use the solidus (~/~), the exp function, or 
-appropriate exponents. Italicize Roman symbols for quantities and variables, 
-but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-sign. Punctuate equations with commas or periods when they are part of a 
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
+% % % % % \section*{References}
 
-Be sure that the 
-symbols in your equation have been defined before or immediately following 
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
-
-\subsection{\LaTeX-Specific Advice}
-
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
-
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
-
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
-
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
-
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
-
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
-
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-An excellent style manual for science writers is \cite{b7}.
-
-\subsection{Authors and Affiliations}\label{AAA}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all conference articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}\label{ITH}
-Headings, or heads, are organizational devices that guide the reader through 
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not 
-topically subordinate to each other. Examples include Acknowledgments and 
-References and, for these, the correct style to use is ``Heading 5''. Use 
-``figure caption'' for your Figure captions, and ``table head'' for your 
-table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-style (in this case, italic) in addition to the style provided by the drop 
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For 
-example, the paper title is the primary text head because all subsequent 
-material relates and elaborates on this one topic. If there are two or more 
-sub-topics, the next level head (uppercase Roman numerals) should be used 
-and, conversely, if there are not at least two sub-topics, then no subheads 
-should be introduced.
-
-\subsection{Figures and Tables}\label{FAT}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-bottom of columns. Avoid placing them in the middle of columns. Large 
-figures and tables may span across both columns. Figure captions should be 
-below the figures; table heads should appear above the tables. Insert 
-figures and tables after they are cited in the text. Use the abbreviation 
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
-
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-\end{tabular}
-\label{tab1}
-\end{center}
-\end{table}
-
-% % % % % \begin{figure}[htbp]
-% % % % % \centerline{\includegraphics{fig1.png}}
-% % % % % \caption{Example of a figure caption.}
-% % % % % \label{fig}
-% % % % % \end{figure}
-
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-rather than symbols or abbreviations when writing Figure axis labels to 
-avoid confusing the reader. As an example, write the quantity 
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-units in the label, present them within parentheses. Do not label axes only 
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-quantities and units. For example, write ``Temperature (K)'', not 
-``Temperature/K''.
-
-\section*{Acknowledgment}
-
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
-
-\section*{References}
-
-Please number citations consecutively within brackets \cite{b1}. The 
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-
-Number footnotes separately in superscripts. Place the actual footnote at 
-the bottom of the column in which it was cited. Do not put footnotes in the 
-abstract or reference list. Use letters for table footnotes.
-
-Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that have not been published, even if they have been 
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-Capitalize only the first word in a paper title, except for proper nouns and 
-element symbols.
-
-For papers published in translation journals, please give the English 
-citation first, followed by the original foreign-language citation \cite{b6}.
-
-\begin{thebibliography}{00}
-\bibitem{b1} G.
-Eason, B.
-Noble, and I.
-N.
-Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
-Trans.
-Roy.
-Soc.
-London, vol.
-A247, pp.
-529--551, April 1955.
-\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-\bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
-\bibitem{b8} D. P. Kingma and M. Welling, ``Auto-encoding variational Bayes,'' 2013, arXiv:1312.6114. [Online]. Available: https://arxiv.org/abs/1312.6114
-\bibitem{b9} S. Liu, ``Wi-Fi Energy Detection Testbed (12MTC),'' 2023, gitHub repository. [Online]. Available: https://github.com/liustone99/Wi-Fi-Energy-Detection-Testbed-12MTC
-\bibitem{b10} ``Treatment episode data set: discharges (TEDS-D): concatenated, 2006 to 2009.'' U.S.
-Department of Health and Human Services, Substance Abuse and Mental Health Services Administration, Office of Applied Studies, August, 2013, DOI:10.3886/ICPSR30122.v2
-\bibitem{b11} K. Eves and J. Valasek, ``Adaptive control for singularly perturbed systems examples,'' Code Ocean, Aug. 2023. [Online]. Available: https://codeocean.com/capsule/4989235/tree
-\end{thebibliography}
-
-\vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
+\bibliographystyle{IEEEtran}
+\bibliography{paper-icict24-automatic_summarisation_of_zambian_legislative_documents}
 

### 2024-09-23 paper-icict24-automatic_summarisation_of_zambian_legislative_documents.tex
Methodology Section
Added content to Methodology section

@@
 %
-% Sepetmber 23 2024
+% Sepetmber 23, 2024
 \usepackage{cleveref}
+%
+
+%
+%
+% September 23, 2024
+\usepackage{enumitem}
+%
 
@@
 The majority of the human evaluators had a preference for the abstractive summarisation model, indicating that its brevity, simplicity, and directness as reasons for their choice.
-In addition, the results of the abstractive summarisation model were stated as being easier to understand..
+In addition, the results of the abstractive summarisation model were stated as being easier to understand.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-component, formatting, style, styling, insert.
+document summarisation, legislative documents, natural language processing, zambia.
 \end{IEEEkeywords}
@@
 \label{sec:methodology}
-Xxxxx xxxxx xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx.
+A mix-methods approach was employed to conduct the studies outlined in this paper as follows:
+\begin{itemize}
+    \item A survey, outlined in \Cref{sec:methodology:understanding_legislation_documents} was conducted with students at University X
+    \item NLP summarisation models were implemented as outlined in \Cref{sec:methodology:summarisation_models_implementaiton}
+    \item A controlled comparative evaluation was performed with human evaluators, as outlined in \Cref{sec:methodology:summarisation_models_analysis}, in order to determine the perceived effective summarisation technique
+\end{itemize}
+
+\subsection{Understanding Legislative Documents}
+\label{sec:methodology:understanding_legislation_documents}
+In order to understand participants' with legislative documents and, additionally, challenges associated with comprehending legislative documents, a survey was conducted with randomly sampled full-time undergraduate students at The University of Zambia.
+Socialdemographic factors---gender, age, school/faculty, programme of study and year of study---were collected from participants, in addition frequency with which legislative documents were accessed and, finally, difficulties with comphrehending legislative documents using "Statutory Instrument No.
+12 of 2018"---shown in \Cref{fig:methodology:understanding_legislation_documents:si18_2018}---as a reference.
+
+\begin{figure*}%%%%%[htbp]
+\fbox{%
+\scalebox{0.315}{\includegraphics{figures/img-icict24-statutory_instrument12_2018.eps}}
+}%
+\caption{Statutory Instrument 18 of 2018: Street Vending and Nuisances.}
+\label{fig:methodology:understanding_legislation_documents:si18_2018}
+\end{figure*}
+
+\subsection{Summarisation Models: Design and Implementation}
+\label{sec:methodology:summarisation_models_implementaiton}
+The implementation of the NLP summarisation models and pipelines was guided by the Cross-industry Standard Process for Data Mining (CRISP-DM) model \cite{Wirth2000CRISPDM}, with the six (6) phases used as follows:
+\begin{enumerate}[label=\textbf{Phase \arabic*.}, leftmargin=*]
+    \item Business Understanding---Acts and Bills available on the National Assembly of Zambia Website were analysed to understand the structure of legislative documents
+    \item Data Understanding---Data sources were identified, with data extraction conducted on publicly available PDF documents
+    \item Data Preparation---Data was pre-processed using common text pre-processing techniques
+    \item Modelling---NLP models were implemented in order to summarise legislative documents
+    \item Evaluation---Human evaluators were used to determine the most effective summarisation technique---abstractive and extractive summarisation
+    \item Deployment---A simple Web-based interface was implemented to comparatively evaluate the two abstractive and extractive summarisations models.
+\end{enumerate}
+
+In order to implement effective NLP summarisation models, focus group discussions were held with University of Zambia Law students, in order to understand elements that comprise legislative documents.
+
+Two NLP summarisation models were implemented use two common summarisation techniques: abstractive summarisation and extractive summarisation.
+
+\subsection{Summarisation Models: Comparative Analysis}
+\label{sec:methodology:summarisation_models_analysis}
+In order to comparatively evaluate the abstractive and extractive summarisation models, a controlled experiment was conducted with human evaluators.
+
+\subsubsection{Task Design}
+\label{sec:methodology:summarisation_models_analysis:task_design}
+The National Pension Scheme Act No. 1 of 2023\footnote{https://www.parliament.gov.zm/node/11020} was used as input to the two summarisation models and corresponding summaries generated.
+
+\subsubsection{Experimental Design}
+\label{sec:methodology:summarisation_models_analysis:experimental_design}
+A comparative analysis between the abstractive summarisation model and extractive summarisation model was performed.
+The study was conducted using a within-subject design, with counterbalancing applied by altering the summarisation models they initially read and rated.
+
+\subsubsection{Procedure}
+\label{sec:methodology:summarisation_models_analysis:procedure}
+Each participant was required to sign a consent form and subsequently required to read the "National Pension Scheme Act No.
+1 of 2023" document and, additionally, the two corresponding summaries.
+Finally, participants were required to complete a questionnaire design to evaluate the following:
+\begin{itemize}
+    \item Relevance of each of the two summaries, relative to the original document
+    \item Readability ofeach of the two summaries
+    \item Prefered summary, when comparing the two generated summaries
+\end{itemize}
 

### 2024-09-23 paper-icict24-automatic_summarisation_of_zambian_legislative_documents.tex
Introduction Section
Added research objectives to the Introduction
section

@@
 
+The main objective of the study presented in this paper was to develop an automated summarisation system that utilises the potential of Natural Language Processing (NLP) to greatly enhance the accessibility and understanding of legislative documents in Zambia for the broader population.
+The specific objectives of the study were as follows:
+\begin{itemize}
+    \item To determine the challenges that people have in understanding legal documents
+    \item To design and implement NLP models for summarising legislative documents
+    \item To evaluate the effectiveness of the natural language processing model
+\end{itemize}
+
 This paper is organised as follows: \Cref{sec:introduction} provides context and background information associated with the studies conducted; \Cref{sec:related_work} comprehensively discusses existing work; \Cref{sec:methodology} outlines the methodological approaches employed when conducting the studies; \Cref{sec:results_and_discussion} discusses the findings and, finally, \Cref{sec:conclusion} outlines concluding remarks and potential future work.
@@
 
+\begin{figure}%%%%%[htbp]
+\fbox{%
+\scalebox{0.65}{\includegraphics{figures/img-icict24-summary1_output.png}}
+}%
+\caption{Summmary 1: .}
+\label{fig:results_and_discussion:summarisation_models:summary1}
+\end{figure}
+
+\begin{figure}%%%%%[htbp]
+\fbox{%
+\scalebox{0.325}{\includegraphics{figures/img-icict24-summary2_output.png}}
+}%
+\caption{Summmary 2: .}
+\label{fig:results_and_discussion:summarisation_models:summary2}
+\end{figure}
+
 \section{Conclusions and Future Work}

### 2024-09-23 paper-icict24-automatic_summarisation_of_zambian_legislative_documents.tex
Related Work Section
Added content to Related Work section

@@
 \label{sec:related_work}
-Xxxxx xxxxx xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx.
+
+\subsection{Legislative Document Complexities}
+\label{sec:related_work:challenges}
+
+The specific challenges associated with comprehending legislative documents are discused by Masson and Tahir, where they place emphasis on interpretation of legal information \cite{Masson2016Legal}.
+The study by Masson and Tahir highlighted the difficulties with accessing legal documents being linked to administrative, financial and technique barriers.
+In addition, the study identified common sources of legislative documents, such as National Assembly.
+More significantly, however, one of the findings from the study was the difficulties Civil Society Organisations face interpreting legal and legislative documents.
+
+This paper proposes an automated approach to interpretating and hence summarising legislative documents.
+
+\subsection{Legislative Document Summarisation}
+\label{sec:related_work:summarisation_techniques}
+There are two classical techniques that are used during document summarisation: abstractive summarisation and extracting summarisation.
+Abstractive summarisation techniques generate summaries which capture the main information and meaning of textual input using new text, while extractive summarisation functions by identifying important elements from the original text \cite{Mehta2016Extractive}.
+
+Numerous studies have been conducted to explore effective techniques for summarising document, with automatic summarisation applied on scientific articles \cite{Altmami2022Automatic}, new articles \cite{Oliveira2024Assessing} and medical documents \cite{Sarker2012Extractive}.
+
+Automatic summarisation has also been applied to legal documents \cite{Hachey2006Extractive} and, more specifically, legislative document; for instance Kornilova and Eidelman \cite{Kornilova2019Billsum} benchmark extractive technques on BillSum, a dataset for summarisation of US Congressional and Carlifonia state bills with their results demonstrating the potential of transfer learning.
+
+The work presented in this paper focuses on legislative documents prepared adn formated by the National Assembly of Zambia, presenting unique challenges specific to this context.
+
+\subsection{Document Summarisation Evaluation}
+\label{sec:related_work:evaluation}
+Evaluation of document summarisation primarily uses two approaches: automatic summarisation techniques and human evaluation \cite{Steinberger2009Evaluation}.
+Automatic evaluation largely uses traditional metrics such as ROUGE\footnote{https://huggingface.co/spaces/evaluate\-metric/rouge} or BERTScore\footnote{https://huggingface.co/spaces/evaluate\-metric/bertscore}, while human evlauation approaches largely focus on subjective quality of resulting text.
+
+The work presented in the paper employed human evaluation techniques as the primary goal was to assess the comprehensiveness of summaries, comparatively.
 
@@
 \fbox{%
-\scalebox{0.325}{\includegraphics{figures/img-icict24-summary2_output.png}}
+\scalebox{0.345}{\includegraphics{figures/img-icict24-summary2_output.png}}
 }%

### 2024-09-23 paper-icict24-automatic_summarisation_of_zambian_legislative_documents.tex
Results and Discussion Section
Added content to Results and Discussion section

@@
 \label{sec:results_and_discussion}
-Xxxxx xxxxx xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx.
+
+\subsection{Understanding Legislative Documents}
+\label{sec:results_and_discussion:challenges}
+
+The survey gathered responses from 126 undergraduate students, primarily falling within the
+18-25 age group, with a mix of participants from various schools and programs of study.
+Notably, Humanities and Social Sciences and Veterinary Medicine constituted the majority of
+participants. The survey covered students from different study years, with a substantial
+representation from Year 2 and Year 3.
+
+The results indicate that a significant portion of participants (98.4\%) have interacted with
+Zambian legislative documents, though the frequency varied. The participants provided
+diverse responses regarding their overall understanding of legal documents, with the majority
+falling within the mid-range on a scale of 1-5.
 
@@
 \fbox{%
-\scalebox{0.65}{\includegraphics{figures/img-icict24-summary1_output.png}}
+\scalebox{0.425}{\includegraphics{figures/img-icict24-factors_affecting_legislative_documents.eps}}
 }%
-\caption{Summmary 1: .}
+\caption{Summmary 2: .}
+\label{fig:results_and_discussion:challenges:challenges}
+\end{figure}
+
+Participants highlighted various challenges in understanding legal documents, as shown in \Cref{fig:results_and_discussion:challenges:challenges}, including
+complex legal terminology, lengthy sentences, unclear or ambiguous language, lack of
+familiarity with legal concepts, and difficulty interpreting legal jargon. These challenges
+point to potential barriers that may hinder effective comprehension of legislative materials.
+
+\begin{figure}%%%%%[htbp]
+\fbox{%
+\scalebox{0.415}{\includegraphics{figures/img-icict24-factors_affecting_legislative_documents_extent.eps}}
+}%
+\caption{Summmary 2: .}
+\label{fig:results_and_discussion:challenges:understanding}
+\end{figure}
+
+Factors such as complex legal terminology, lengthy sentences, unclear language, lack of
+familiarity with legal concepts, and difficulty interpreting legal jargon were identified as
+influencing participants' understanding of legal documents, as shown in \Cref{fig:results_and_discussion:challenges:understanding}. These insights underscore the
+need for targeted interventions to address these specific challenges
+
+Participants provided valuable comments and suggestions, emphasising the importance of
+brevity and clarity in legal documents. Recommendations included minimising lengthy
+sentences, avoiding technical jargon, and making legal documents more accessible.
+
+The survey conducted at the University of Zambia sheds light on the challenges
+undergraduate students face in understanding legal documents. The findings indicate a
+diverse range of difficulties, encompassing language complexity, sentence structure, and a
+lack of familiarity with legal concepts. The insights from this study pave the way for potential
+improvements in legal document accessibility and comprehension. The use of automatic
+summarization software is suggested as a possible solution to address these challenges,
+providing concise and clear summaries of legislative materials.
+
+\subsection{Automatic Summarisation}
+\label{sec:results_and_discussion:automatic_summarisation}
+
+\subsubsection{Data Extraction and Pre-processing}
+\label{sec:results_and_discussion:automatic_summarisation:data_extraction}
+The Python programming language\footnote{https://www.python.org} was used to implement the summarisation models.
+A two-step process was used to extract data from PDF documents for the purpose of preparing it for subsequent data cleaning.
+The primary library used for this extraction was PyMuPDF\footnote{https://github.com/pymupdf/PyMuPDF}, specifically the fitz module.
+This library allows for efficient handling of PDF documents in Python.
+
+In order to use a standardised representation of textual input, case folding was applied to input text.
+
+\subsubsection{Extractive Summarisation Model}
+\label{sec:results_and_discussion:automatic_summarisation:extractive}
+
+The evolution of word embedding models progressed with Mikolov et al., who introduced the word2vec model based on skip-grams.
+This model extended our understanding of word relationships by considering complex
+associations, including opposites, tenses, plurals, and phrases. Here, the SpaCy\footnote{https://spacy.io} library plays a
+pivotal role in text processing, aiding in the identification and removal of stop words and
+punctuation.
+
+\Cref{fig:results_and_discussion:summarisation_models:summary1} illustrates a sample output for the abstractive summarisation model.
+
+\begin{figure}%%%%%[htbp]
+\fbox{%
+\scalebox{0.65}{\includegraphics{figures/img-icict24-summary1_output.eps}}
+}%
+\caption{Summmary 1: Extractive Summarisation.}
 \label{fig:results_and_discussion:summarisation_models:summary1}
+\end{figure}
+
+\subsubsection{Abstractive Summarisation Model}
+\label{sec:results_and_discussion:automatic_summarisation:abstractive}
+
+The abstractive summarisation model was implemented using the BART model from the Hugging Face Transformers library. The
+code utilized the "transformers" library to import the necessary components, including the pipeline for text generation, the BART tokenizer, and the BART model for conditional generation.
+Within the "abstractive\_summarize" function, the pre-trained BART model and tokenizer were loaded using the specified model name "facebook/bart-large-cnn".
+The input text was then tokenized, and the summary was generated using the BART model.
+The "generate" method of the model was utilized to produce the summary, with parameters such as maximum and minimum length, length penalty, number of beams, and early stopping specified to control the summarization process.
+This approach proved to be successful in producing abstractive summaries with the BART model, leveraging its capabilities for text generation and summarization.
+
+\Cref{fig:results_and_discussion:summarisation_models:summary2} illustrates a sample output for the abstractive summarisation model.
+
+\begin{figure}%%%%%[htbp]
+\fbox{%
+\scalebox{0.345}{\includegraphics{figures/img-icict24-summary2_output.eps}}
+}%
+\caption{Summmary 2: Abstractive Summarisation.}
+\label{fig:results_and_discussion:summarisation_models:summary2}
+\end{figure}
+
+By integrating both extractive and abstractive techniques, this project aimed to provide a comprehensive understanding of Zambian legislative materials.
+The use of diverse Python libraries, including SpaCy for extractive summarization and Transformers BART Model for abstractive summarization, showcased a multifaceted approach to effectively distill and present critical information from lengthy legal documents.
+
+\subsection{Human Comparative Evaluation}
+\label{sec:results_and_discussion:human_evaluation}
+
+\begin{figure}%%%%%[htbp]
+\fbox{%
+\scalebox{0.425}{\includegraphics{figures/img-icict24-summary1-relevance.eps}}
+}%
+\caption{Summmary 1: Relevance.}
+\label{fig:results_and_discussion:summarisation_models:summary1_relevance}
+\end{figure}
+
+The purpose of this evaluation was to assess the effectiveness of automatic summarization techniques applied to Zambian legislative documents.
+The participants were asked to read two summaries (Summary 1 - extractive summary, and Summary 2 - abstractive summary) generated from the original legislative document.
+The evaluation focused on relevance, readability, and preference for conveying information.
+
+\begin{figure}%%%%%[htbp]
+\fbox{%
+\scalebox{0.425}{\includegraphics{figures/img-icict24-summary2-relevance.eps}}
+}%
+\caption{Summmary 2: Relevance.}
+\label{fig:results_and_discussion:summarisation_models:summary2_relevance}
+\end{figure}
+
+A total of nine participants participated in the comparative evaluation.
+
+The majority of participants who preferred Summary 2 cited its brevity, simplicity, and directness as reasons for their choice.
+Participants mentioned that Summary 2 was easier to understand and more straightforward.
+One participant specifically noted that Summary 2 was "straight to the point," enhancing quick comprehension.
+two participants provided feedback, with one expressing a positive sentiment, stating, "This is good." The other participant did not provide specific comments.
+
+The evaluation indicates a strong preference for Summary 2, the abstractive summary, among participants.
+While both summaries received similar ratings for relevance and readability, the brevity and directness of Summary 2 seemed to resonate more with participants.
+The positive feedback aligns with the project's goal of enhancing the accessibility of Zambian legislative information through automatic summarization.
+
+In the relevance evaluation, for the extractive summary (Summary 1), participants rated it between 3 and 8, with none selecting 1, 2, 9, or 10.
+Similarly, for the abstractive summary (Summary 2), ratings ranged from 3 to 10, with no
+participants choosing 1 or 2. In terms of readability, both summaries achieved average scores
+around 4.5, reflecting moderate levels of readability.
+Significantly, the majority of participants (88.9\%) expressed a preference for Summary 2, citing its brevity, simplicity, and directness as reasons for their choice.
+This preference aligns with the feedback received, where participants highlighted that Summary 2 was easier to understand and more straightforward, with one participant specifically noting that it was "straight to the point," facilitating quick comprehension.
+Out of the two participants who provided feedback, one expressed a positive sentiment, stating, "This is good," while the other did not provide specific comments.
+
+\begin{figure}%%%%%[htbp]
+\fbox{%
+\scalebox{0.425}{\includegraphics{figures/img-icict24-summary1-readability.eps}}
+}%
+\caption{Summmary 1: Readability.}
+\label{fig:results_and_discussion:summarisation_models:summary1_readability}
 \end{figure}
@@
 \fbox{%
-\scalebox{0.345}{\includegraphics{figures/img-icict24-summary2_output.png}}
+\scalebox{0.425}{\includegraphics{figures/img-icict24-summary2-readability.eps}}
 }%
-\caption{Summmary 2: .}
-\label{fig:results_and_discussion:summarisation_models:summary2}
+\caption{Summmary 2: Readability.}
+\label{fig:results_and_discussion:summarisation_models:summary2_readability}
 \end{figure}
@@
 \label{sec:conclusion}
-Xxxxx xxxxx xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx  xxxxx.
+The imperative for automating the summarization of Zambian Legislative Documents becomes evident as it presents an opportunity for citizens to gain quick and enhanced comprehension of lengthy legal documents, including Acts of Parliament.
+This study aimed at identifying challenges in understanding legislative documents, developing and implementing
+an NLP model for automatic summarization, and assessing the model's effectiveness.
+The evaluation underscores the efficiency of abstractive summarization techniques, particularly noting participant preference in conveying information.
+These findings offer valuable insights into the strengths and preferences of various summarization approaches, guiding future initiatives to improve the accessibility and understanding of Zambian legislative documents.
 
